---
title: "Mini Data-Analysis Deliverable 1"
output: github_document
---

# Welcome to your (maybe) first-ever data analysis project!

And hopefully the first of many. Let's get started:

1.  Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

<!-- -->

    install.packages("devtools")
    devtools::install_github("UBC-MDS/datateachr")

2.  Load the packages below.

```{r}
library(datateachr)
library(tidyverse)
```

3.  Make a repository in the <https://github.com/stat545ubc-2024> Organization. You can do this by following the steps found on canvas in the entry called [MDA: Create a repository](https://canvas.ubc.ca/courses/158528/pages/mda-create-a-repository). One completed, your repository should automatically be listed as part of the stat545ubc-2024 Organization.

# Instructions

## For Both Milestones

-   Each milestone has explicit tasks. Tasks that are more challenging will often be allocated more points.

-  Each milestone will be also graded for reproducibility, cleanliness, and coherence of the overall Github submission. 

- While the two milestones will be submitted as independent deliverables, the analysis itself is a continuum - think of it as two chapters to a story. Each chapter, or in this case, portion of your analysis, should be easily followed through by someone unfamiliar with the content. [Here](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R.html) is a good resource for what constitutes "good code". Learning good coding practices early in your career will save you hassle later on!

- The milestones will be equally weighted. 

## For Milestone 1

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-1.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work below --->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to the mini-analysis GitHub repository you made earlier, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 36 points: 30 for your analysis, and 6 for overall reproducibility, cleanliness, and coherence of the Github submission. 

# Learning Objectives

By the end of this milestone, you should:

-   Become familiar with your dataset of choosing
-   Select 4 questions that you would like to answer with your data
-   Generate a reproducible and clear report using R Markdown
-   Become familiar with manipulating and summarizing your data in tibbles using `dplyr`, with a research question in mind.

# Task 1: Choose your favorite dataset 

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

-   *apt_buildings*: Acquired courtesy of The City of Toronto's Open Data Portal. It currently has 3455 rows and 37 columns.

-   *building_permits*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 20680 rows and 14 columns.

-   *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

-   *flow_sample*: Acquired courtesy of The Government of Canada's Historical Hydrometric Database. It currently has 218 rows and 7 columns.

-   *parking_meters*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 10032 rows and 22 columns.

-   *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

-   *vancouver_trees*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 146611 rows and 20 columns.

**Things to keep in mind**

-   We hope that this project will serve as practice for carrying our your own *independent* data analysis. Remember to comment your code, be explicit about what you are doing, and write notes in this markdown document when you feel that context is required. As you advance in the project, prompts and hints to do this will be diminished - it'll be up to you!

-   Before choosing a dataset, you should always keep in mind **your goal**, or in other ways, *what you wish to achieve with this data*. This mini data-analysis project focuses on *data wrangling*, *tidying*, and *visualization*. In short, it's a way for you to get your feet wet with exploring data on your own.

And that is exactly the first thing that you will do!

1.1 **(1 point)** Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:

**Note**: We encourage you to use the ones in the `datateachr` package, but if you have a dataset that you'd really like to use, you can include it here. But, please check with a member of the teaching team to see whether the dataset is of appropriate complexity. Also, include a **brief** description of the dataset here to help the teaching team understand your data.

<!-------------------------- Start your work below ---------------------------->

1: *apt_buildings*\
2: *building_permits*\
3: *steam_games*\
4: *cancer_sample*

<!----------------------------------------------------------------------------->

1.2 **(6 points)** One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*.

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you below, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

<!-------------------------- Start your work below ---------------------------->

## Exploring the Dataset

### steam_games
```{r}
#procure basic information
glimpse(steam_games)
```

By inspection, the dataset *steam_games* contains `r nrow(steam_games)` observations and `r ncol(steam_games)` variables of interest. Among the variables, `r sum(sapply(steam_games, is.numeric))` are numerical (*id*, *original_price*, *discount_price*, *achievements*), and the remaining are all encoded as strings. There are also 5 non-numeric variables that contain some numerical information:  *release_date*, *minimum_requirements*, *recommended_requirements*, *recent_reviews*, *all_reviews*.

Moreover, by inspection, at least some (*achievements*, *mature_content*, *discount_price*, *original_Price*) of the variables takes on a value of NA for certain observations.


```{r}
#Segregating the observations with NA
steam_games_without_NA <- filter(steam_games, complete.cases(steam_games))
glimpse(steam_games_without_NA)
```

By filtering for only incomplete observations, we see that the dataset only contains `r nrow(steam_games_without_NA)` games with full data and no missing values, this is not a large number


```{r}

#Identify number of NAs in each column
colSums(is.na(steam_games))

#Find observations with missing names
steam_games_no_names <- filter(steam_games, is.na(name))
glimpse(steam_games_no_names)
```

From the above output, it is clear that the vast majority (around `r mean(sum(sapply(steam_games$mature_content, is.na)), sum(sapply(steam_games$recent_reviews, is.na)))`) of the total 40833 observations have missing values for the *mature_content* and *recent_reviews*. This may not be unreasonable as certain games may contain no mature content and may also have no recent reviews.

A minority (around `r mean(sum(sapply(steam_games$minimum_requirements, is.na)), sum(sapply(steam_games$recommended_requirements, is.na)))`) of the observations have no information on *minimum_requirements* or *recommended_requirements*.

Curiously, there are `r nrow(steam_games_no_names)` games that has a missing value for the *name* variable. Upon a quick inspection of these two rows, it appears from their *url* that these observations are for the general steam store page and steam gift cards and are not games per se.

### cancer_sample

```{r}
#procure basic information
glimpse(cancer_sample)
```

By inspection, the dataset *cancer_sample* contains `r nrow(cancer_sample)` observations and `r ncol(cancer_sample)` variables of interest. Among the variables, `r sum(sapply(cancer_sample, is.numeric))` are numerical. This gives us `r ncol(cancer_sample) - sum(sapply(cancer_sample, is.numeric))` non-numeric variables.

The only non-numerical variable in question is *diagnosis*.

By inspection, there does not appear to be observations with missing values.

```{r}
#Verify the completeness of data
number_of_complete_cases <- nrow(filter(cancer_sample, complete.cases(cancer_sample)))
number_of_complete_cases == nrow(cancer_sample)
```

Some R code enable us to verify that the *cancer_sample* have `r nrow(cancer_sample) - number_of_complete_cases` rows with missing values.

```{r}
#Getting the possible outcomes for diagnosis
unique(cancer_sample$diagnosis)

#Checking the distribution
counts = count(cancer_sample, diagnosis)
counts
```

The only non-numerical variable in the dataset, *diagnosis* is categorical with `r length(unique(cancer_sample$diagnosis))` categories, "M" and "B". These are in reference to the neoplasm being malignant or benign.

There are a total of `r counts[1,2]` benign cases and a total of `r counts[2,2]` malignant cases.

### apt_buildings

```{r}
#procure basic information
glimpse(apt_buildings)
```

By inspection, the dataset *apt_buildings* contains `r nrow(apt_buildings)` observations and `r ncol(apt_buildings)` variables of interest. Among the variables, `r sum(sapply(apt_buildings, is.numeric))` are numerical. This gives us `r ncol(apt_buildings) - sum(sapply(apt_buildings, is.numeric))` non-numeric variables. 

Moreover, most of the non-numeric variables are categorical and appears to only take on the values of "YES" and "NO". These include the variables *sprinkler_system*, *separate_water_meters*, *cooling_room*, and several others. There are also some that do not take on strict categories, such as *site_address*. It is unclear at first glance whether *facilities_available* and *amentities* are categorical or descriptive.

There also appear to be some observations with missing values.

```{r}
#Segregating the observations with NA
apt_buildings_without_NA <- filter(apt_buildings, complete.cases(apt_buildings))
glimpse(apt_buildings_without_NA)
```

By filtering for only incomplete observations, we see that the dataset only contains `r nrow(apt_buildings_without_NA)` games with full data and no missing values.

```{r}
#Unique values of amenities
unique(apt_buildings$amenities)
amentities_types = length(unique(apt_buildings$amenities))
```
It seems that for the *amenities* variable, it can take on a total of `r amentities_types` possible values, including NA. By visually inspecting the output of the code above, it appears that the values of this variable consist of tuple of several unique strings, including *In/Outdoor rec facilities*, *In/Outdoor pool*, *In/Outdoor exercise room*, *Child play area*, and *Sauna*.

### building_permits

```{r}
#procure basic information
glimpse(building_permits)
```

By inspection, the dataset *building_permits* contains `r nrow(building_permits)` observations and `r ncol(building_permits)` variables of interest. Among the variables, `r sum(sapply(building_permits, is.numeric))` are numerical. This gives us `r ncol(building_permits) - sum(sapply(building_permits, is.numeric))` non-numeric variables.

In the output above, the variables *property_use*, *specific_use_category*, and *type_of_work* appears to be categorical whilst the remaining non-numeric variables seem to be descriptive and does not take on finitely many categories.

Moreover, there seems to be a large number of missing values surrounding *project_description*.

```{r}
#Counting the number of NAs in project description
project_desc_NA <- sum(sapply(building_permits$project_description, is.na))

#Finding the total number of full observations
building_permits_without_NA <- filter(building_permits, complete.cases(building_permits))
glimpse(building_permits_without_NA)

#Finding the total number of full observations, ignoring project_description
building_permits_without_NA_no_desc <- filter(building_permits[-6], complete.cases(building_permits[-6]))
glimpse(building_permits_without_NA_no_desc)

```

In particular, `r project_desc_NA` observations do not have a *project_description*. Overall, we have `r nrow(building_permits_without_NA)` full observations.

If we ignore *project_description*, there are `r nrow(building_permits_without_NA_no_desc)` full observations.

```{r}
#Inspecting projects of value zero
building_permits_value_0 = filter(building_permits, project_value == 0 | is.na(project_value))
glimpse(building_permits_value_0)

#Identifying the type_of_work for such projects
unique(building_permits_value_0$type_of_work)
counts = count(building_permits_value_0, type_of_work)
counts
```

Within this dataset, we also have `r nrow(building_permits_value_0)` projects with a value of 0 or NA. This may be expected for salvage and demolition operations.

Based on the code output above, there are `r length(unique(building_permits_value_0$type_of_work))` types of work for such type of projects. Among these are `r counts[3,2]` instances of new building.

<!----------------------------------------------------------------------------->

1.3 **(1 point)** Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 1. What lead you to choose this one? Briefly explain your choice below.

<!-------------------------- Start your work below ---------------------------->

I will be using the **apt_buildings** dataset, as this dataset contains a relatively large number of column and include a good mix of both categorical and numerical variables, percent being numerical. This is unlike **steam_games** or **cancer_sample** which leans heavily in of the two types. **building_permits**, on the other hand, gives a relatively small number of variables to work with.

<!----------------------------------------------------------------------------->

1.4 **(2 points)** Time for a  final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with your dataset. Note it down below.

<!-------------------------- Start your work below ---------------------------->

> How is the building age of an apartment complex related to its amenities, parking spaces, and other features?

<!----------------------------------------------------------------------------->

# Important note

Read Tasks 2 and 3 *fully* before starting to complete either of them. Probably also a good point to grab a coffee to get ready for the fun part!

This project is semi-guided, but meant to be *independent*. For this reason, you will complete tasks 2 and 3 below (under the **START HERE** mark) as if you were writing your own exploratory data analysis report, and this guidance never existed! Feel free to add a brief introduction section to your project, format the document with markdown syntax as you deem appropriate, and structure the analysis as you deem appropriate. If you feel lost, you can find a sample data analysis [here](https://www.kaggle.com/headsortails/tidy-titarnic) to have a better idea. However, bear in mind that it is **just an example** and you will not be required to have that level of complexity in your project.

# Task 2: Exploring your dataset 

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE under Task 3**.

2.1 **(12 points)** Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. 

Make sure that you're using dplyr and ggplot2 rather than base R for this task. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

1.  Plot the distribution of a numeric variable.
2.  Create a new variable based on other variables in your data (only if it makes sense)
3.  Investigate how many missing values there are per variable. Can you find a way to plot this?
4.  Explore the relationship between 2 variables in a plot.
5.  Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6.  Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7.  Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8.  Use a density plot to explore any of your variables (that are suitable for this type of plot).

2.2 **(4 points)** For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.

<!-------------------------- Start your work below ---------------------------->

## 1 Introduction

In this mini data analysis, I will be using the dplyr and ggplot2 to explore the various features of the *apt_buildings* data set. Through visualizing and manipulating the this dataset, I aim to produce 4 possible research questions that may be addressed by this dataset.

### 1.1 Loading the Packages

As stated above, the ggplot2 and the tidyverse packages are required for this analysis. They will be loaded here:

```{r}
library(ggplot2)
library(tidyverse)
```

### 1.2 Data Overview

We will begin by producing a summary of the dataset using both the built-in summary function and via the glimpse function from the tidyverse package (this is just a short recapitulation of task 1)
```{r}
glimpse(apt_buildings)
```

Based on the output of the glimpse function, the dataset has `r nrow(apt_buildings)` rows and `r ncol(apt_buildings)` columns. In the variables represented by the columns, `r sum(sapply(apt_buildings, is.numeric))` are numerical. This gives us a total of `r ncol(apt_buildings) - sum(sapply(apt_buildings, is.numeric))` variables that are not numerical.

It is also clear that some observations have missing values.

### 1.3 The Missing Values (task 3)

Having mentioned that there are numerous missing values in this dataset, we will now try to identity how many missing values there are per variable.

```{r}
#Create a new tibble that includes the number of NA observations for each column
missingness <- apt_buildings %>%
  summarise_all(~ sum(is.na(.)))
glimpse(missingness)
```

Using the summarise_all function from dplyr, we have produced a table that documents the number of NAs in each of the variables. In particular, it appears that we have `r missingness$prop_management_company_name` observations with no value for  *prop_management_company_name* and `r missingness$amenities` observations with no information on amenities.

It seems that, among all the variables, only *id, bike_parking, property_type, rsn, site_address, war, no_of_storeys, no_of_units*, and *facilities_available* have 0 missing values. Below, I have included three plots that showcases the number of missing values for each variable.

```{r}
#Create a new tibble showing the number fo missing variables
variable <- colnames(missingness)
number_missing <- data.frame(t(missingness))$t.missingness
id <- seq(1, length(variable))

missingness_plot <- as_tibble(cbind(id, variable, number_missing))
missingness_plot <- mutate(missingness_plot, number_missing = as.numeric(number_missing))

#Creating the plots
missingness_plot[1:12,] %>%
  ggplot(aes(variable, colour = variable)) +
  geom_bar(aes(weight = number_missing)) +
  ylab("Number of missing values Plot 1") +
  ggtitle("Number of missing values (First 12 variables)") +
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
  xlab("Variables") +
  theme(legend.position="bottom", legend.text = element_text(size = 6.5)) 
  
missingness_plot[13:24,] %>%
  ggplot(aes(variable, colour = variable)) +
  geom_bar(aes(weight = number_missing)) +
  ylab("Number of missing values Plot 1") +
  ggtitle("Number of missing values (Middle 12 variables)") +
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
  xlab("Variables") +
  theme(legend.position="bottom", legend.text = element_text(size = 6.5)) 

missingness_plot[25:37,] %>%
  ggplot(aes(variable, colour = variable)) +
  geom_bar(aes(weight = number_missing)) +
  ylab("Number of missing values Plot 1") +
  ggtitle("Number of missing values (Last 13 variables)") +
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
  xlab("Variables") +
  theme(legend.position="bottom", legend.text = element_text(size = 6.5))

```

### 1.4 Identifying the building age (task 2)

For the purpose of this analysis, in addition to the number of elevators (*no_of_elevators*), we are also interested in elevator availability, which could be captured by a new variables:

- The number of elevator per unit (elevator_density)

Moreover, we are also interested in the age of the building. Although it is captured by the variable *building age*, it would be best if it is included in a more straight forward manner, which requires yet another new variable:

- The age of the building as of 2025 (building_age)

We will create the new variables using the code below:

```{r}
#Create a new tibble with the variables mentioned above
apt_buildings_new <- apt_buildings
apt_buildings_new <- mutate(apt_buildings_new, elevator_density = 
                              no_of_elevators / no_of_units, building_age = 
                              2025 - year_built)

#producing a numerical summary of the new variables

summary(c(apt_buildings_new$building_age))
summary(c(apt_buildings_new$elevator_density))
```

### 1.5 Relationship between no_of_storeys and building_age (Task 4)

It is expected that buildings of various age would be built with different features. For example, improvement in engineering technologies and materials enabled the construction of apartments with more storeys. To confirm this intuition, we will make use of a scatter plot between the new variable *building_age* and *no_of_storeys*.


```{r}
#Creating the scatter plot

apt_buildings_new %>% 
  ggplot(aes(x = building_age, y = no_of_storeys)) +
  geom_point(size = 0.2, col ="red") +
  #Adding an ordinary least square line of best fit
  geom_smooth(method = "lm") +
  ylim(c(0, 60)) +
  ggtitle("Building age vs. Number of Storeys") +
  xlab("Building Age as of 2025") +
  ylab("Number of Storeys")
```

Based on the above plot, it is clear that, as building age increases, the number of storeys decreases. Moreover, based on the plot, it is apparent from the density of points that most buildings studied in the dataset were constructed around 40-60 years ago. It also appears that most tall apartments were built either around 50 years ago or after the 2000s.

### 1.6 Distribution of Number of units (Task 1)

Continuing the earlier discussion on the number of storeys. I also suspect that taller buildings ought to be furnished with more sets of elevators. As such, to confirm this, I will be plotting the distribution of *no_of_storeys* across each possible value for *no_of_elevators* in a ridge-plot.

To find the appropriate bins for *no_of_elevators* in the ridge plot, we need to make sure that for each level in *no_of_elevators* we have enough obseravtions to plot a distribution, let us first observe this variable's count.

```{r}
elevator_count <- count(apt_buildings_new, no_of_elevators)
glimpse(elevator_count)
```

From the tibble above, it appears that for buildings with *no_of_elevators* equaling 7, 15, or 32, we only have 1 observation. This will not be sufficient for plotting the distribution. Thus, we will first filter out observations with *no_of_elevators* $\geq 7$

```{r}
#creatign the box plot
apt_buildings_new %>% 
  filter(no_of_elevators <= 6) %>%
  ggplot(aes(y = as.factor(no_of_elevators), x = no_of_storeys)) +
  ggridges::geom_density_ridges() +
  ggtitle("Distribution of Number of Storeys") +
  xlab("Number of Storeys") +
  ylab("Number of Elevators")
```

It appears that the *no_of_storeys* indeed has a different distribution depending on the number of elevators. For example, as the number of elevators increase from 1 to 6, both the mean of *no_of_storeys* and its standard deviation also appear to increase steadily. This does follow from my previous line of reasoning.

<!----------------------------------------------------------------------------->

# Task 3: Choose research questions 

**(4 points)** So far, you have chosen a dataset and gotten familiar with it through exploring the data. You have also brainstormed one research question that interested you (Task 1.4).  Now it's time to pick 4 research questions that you would like to explore in Milestone 2! Write the 4 questions and any additional comments below. 

<!--- *****START HERE***** --->

> **Question 1:** What are the most significant factors that influence whether a building would have garbage chutes?

> **Question 2:** In what ways are the availability of car parking spaces and bicycle parking spaces related?

> **Question 3:** Which variables admit a way of effectively predicting whether or not a building has air conditioning?

> **Question 4:** Do larger and more recent buildings have more robust fire safety systems (fire alarm, fire escape, intercom) in place?

<!----------------------------->

# Overall reproducibility/Cleanliness/Coherence Checklist 

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. An example of a major continuity error is having a data set listed for Task 3 that is not part of one of the data sets listed in Task 1. 

## Error-free code (3 points) 

For full marks, all code in the document should run without error. 1 point deduction if most code runs without error, and 2 points deduction if more than 50% of the code throws an error. 

## Main README (1 point)

There should be a file named `README.md` at the top level of your repository. Its contents should automatically appear when you visit the repository on GitHub.

Minimum contents of the README file:

-   In a sentence or two, explains what this repository is, so that future-you or someone else stumbling on your repository can be oriented to the repository.
-   In a sentence or two (or more??), briefly explains how to engage with the repository. You can assume the person reading knows the material from STAT 545A. Basically, if a visitor to your repository wants to explore your project, what should they know?

Once you get in the habit of making README files, and seeing more README files in other projects, you'll wonder how you ever got by without them! They are tremendously helpful.

## Output (1 point)

All output is readable, recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

(0.5 point deduction if any of the above criteria are not met. 1 point deduction if most or all of the above criteria are not met.)

Our recommendation: right before submission, delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant. Then, after your final commit and push to Github, CHECK on Github to make sure that everything looks the way you intended!

## Tagged release (0.5 points)

You've tagged a release for Milestone 1. 

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching.
